### 2013-09-06 talks/colloquium/theory-of-liquids.tex
update talk a bit Tested everything on bingley.
more edits on talk for next week Tested on darcy. Took 0:19.24.

\begin{frame}
  \frametitle{Simple liquids}
  \begin{itemize}
  \item Perturbative attraction added to hard spheres
  \item ``High T expansion''
    \[
    F_\text{disp} = \left(a_1(n) + a_2(n)\beta + \mathcal{O}(\beta^2)\right)n,
    \quad \quad \beta \equiv \frac{1}{k_BT}
    \]

@@

%\subsection{Hydrogen bonding (Association)}
\begin{frame}
  \frametitle{Hydrogen bonds (Association)}
  \vspace{-2em}
  \hfill\includegraphics[width=7cm]{figs/hydrogen-bonds}\hspace{-3em}
  \vspace{-2em}
  \begin{itemize}
  \item Highly directional bonds
  \item Not a ``small'' interaction (around $4k_BT$)
  \item Small volume of interaction
  \item Wertheim's Thermodynamic Perturbation Theory\\ \hfill
    \mycite{Wertheim}{J. Stat. Phys.}{1984,1986}
  \item How often do hard spheres touch?
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Statistical Associating Fluid Theory (SAFT)}
  The above terms combined describe a well-established
  theory for homogeneous liquids such as water.
  \begin{center}
    \vspace{-1em}
    \includegraphics[height=6cm]{../../papers/water-saft/figs/pressure-with-isotherms-truncated}
  \end{center}
  \hfill Clark \emph{et al}, \emph{Mol. Phys.}
  (2006)
\end{frame}

@@

>>>>

\begin{frame}
  \frametitle{Simple liquids}
  \begin{itemize}
  \item Perturbative attraction added to hard spheres
  \item ``High T expansion''
    \[
    F_\text{disp} = N\left(a_1(n) + a_2(n)\beta + \mathcal{O}(\beta^2)\right),
    \quad \quad \beta \equiv \frac{1}{k_BT}
    \]

@@

%\subsection{Hydrogen bonding (Association)}
\begin{frame}
  \frametitle{Hydrogen bonds (Association)}
  \vspace{-2em}
  \hfill\includegraphics[width=7cm]{figs/hydrogen-bonds}\hspace{-3em}
  \vspace{-2em}
  \begin{itemize}
  \item Highly directional bonds
  \item Not a ``small'' interaction (around $4k_BT$)
  \item Small volume of interaction
  \item Wertheim's Thermodynamic Perturbation Theory\\ \hfill
    \mycite{Wertheim}{J. Stat. Phys.}{1984,1986}
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Putting it all together}
  All these terms combined describe SAFT, a well-established theory
  for \emph{homogeneous} liquids such as water.
  \begin{center}
    \vspace{-1em}
    \includegraphics[height=6cm]{../../papers/water-saft/figs/pressure-with-isotherms-truncated}
  \end{center}
  \hfill Clark \emph{et al}, \emph{Mol. Phys.}
  (2006)
\end{frame}

@@

\begin{frame}
  \frametitle{Testing the theory:  Monte Carlo simulation}
  \vspace{-0.8em}
  \begin{center}
    \animategraphics[height=20em]{.6}{anim/mc-slow-}{000}{30}\\
    \vspace{-0.5em}
    hard circles between two walls
  \end{center}
\end{frame}

\begin{frame}
  \frametitle{Testing the theory:  Monte Carlo simulation for $n(\rr)$}
  \vspace{-0.8em}
  \begin{center}
    \animategraphics[height=20em,autoplay]{.6}{anim/mc-density-}{000}{30}\\
    \vspace{-0.5em}
    hard circles between two walls
  \end{center}
\end{frame}
